---
output: pdf_document
---
# my knitr document
Pawel Franczak

## introduction

This is some txt. here is a code chunk below. echo=false hides code
```{r simulation, echo=FALSE}
set.seed(1)
x <- rnorm(100)
mean(x)
```

results='hide' hides results
```{r simulation 2, results='hide'}
set.seed(1)
x <- rnorm(100)
mean(x)
```

###example of inline text computations
```{r computetime,echo=FALSE}
time <- format(Sys.time(), "%a %b %d %X %Y")
rand <- rnorm(1)
```
*the current time is `r time`. favourite random number is `r rand`.*

###incorporating graphics
first simulate some data
```{r simulatedata, echo=TRUE}
x <- rnorm(100); y <- x + rnorm(100, sd = .5)
```
here's a scatterplot
```{r scatterplot, fig.height=4}
par(mar = c(5, 4, 1, 1), las = 1)
plot(x, y, main = 'my simulated data')
```

###making tables with xtable
```{r fitmodel}
library(datasets)
data(airquality)
fit <- lm(Ozone ~ Wind + Temp + Solar.R, data = airquality)
```
here's a table of regression coefficients
```{r showtable, results='asis'}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type = 'html')
```

